Simulation pipeline

### 2021-05-17 Analysis/02_Simulation_pipeline.Rmd
sim pipeline updated

```{r}
## Running the full optimisation
results <- optim.replicate(fun = simulate.facilitation(),
                           diagnose = var,
                           summarise = optim.summarise,
                           minimum = 20, maximum = 100,
                           stop.variance = 0.05,
                           verbose = TRUE,
                           bkp.path = "../Data/Processed/",
                           bkp.name = "sim_facilitation.rda")
```

>>>>

```{r}
## Running the full optimisation
results <- optim.replicate(input.fun = simulate.facilitation,
                           diagnose = var,
                           summarise = optim.summarise,
                           minimum = 20, maximum = 100,
                           stop.variance = 0.05,
                           verbose = TRUE,
                           bkp.path = "../Data/Processed/",
                           bkp.name = "sim_facilitation.rda")
```
